---
title: "Projects"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
devtools::install_github("hadley/emo")
```  
 
A collection of personal projects that i have worked on. A data(tail) of everything from basic cleaning data, to simple data exploration to predictive analytics. Feel free to share your feedback or even contribute (Github) `r emo::ji("smile")`.


# NYC Schools Survey

2021 | 04 | 01 Last compiled: `r Sys.Date()`

[**This project**](https://rickyboshe.github.io/projects/index.html) analyzes the relationship between high school performance and the demographic makeup of schools in New York City. Additionally, a survey of parents, students and teachers perceptions on the quality of schools is analyzed and compared with actual performance. 

<center>
```{r, echo=FALSE, out.width="75%", fig.align="center"}
knitr::include_url("images/Graph.html", height = "350px")
```
</center>

<br><br>

# USA Seafood Analysis

2021 | 04 | 13 Last compiled: `r Sys.Date()`

[**This project**](https://rickyboshe.github.io/projects/Fisheries.html) takes a glimpse at Seafood industry in the USA. As more people are opting against red meat diet for plant based and sea food, this might be a good time to analyze aquatic food sources. The [environmental impact](https://www.greenpeace.org.uk/news/why-meat-is-bad-for-the-environment/#:~:text=It%20causes%20climate%20change,the%20atmosphere%2C%20accelerating%20global%20warming) of industrialized red meat production and [health concerns](https://www.nytimes.com/2019/09/30/health/red-meat-heart-cancer.html) has made sea food a favourable alternative diet also termed as ["pescatarian diet"](https://www.medicalnewstoday.com/articles/323907#:~:text=What%20is%20a%20pescatarian%20diet%3F&text=In%20the%20pescatarian%20diet%2C%20a,and%20fish%20products%20may%20enhance). 

This project looks to answer two thing:

1.  Is seafood environmentally sustainable? 
2.  Does it pack the nutrients to replace red meat diet?

<center>
```{r, echo=FALSE, out.width="90%", fig.align="center"}
knitr::include_url("images/fish.html", height = "700px")
```
</center>


<br></br>
